Topological Equivariant Artist Model for Visualization Library Architecture

### 2022-09-09 paper/main.tex
appendix tables

\subsubsection{Example: Graphic and Data}
\begin{figure}[h!]
  \includegraphics*[width=1\columnwidth]{xi_scatter.png}
  \caption{The functors $\vindex, \vindexpull, \vindexpush$ establish the correspondence between a data section \dsection\ and a graphic generation function \gsection. For every data record $\dsection(\dbasepoint)$, there is a graphic generating function $\vindexpush\gsection = \gsection|_{\vindexpre\dbasepoint}$. This curried function is here represented as the visual parameters associated with that function to demonstrate that it generates the visual element for that data record. Every data section can also be copied over to the graphic space such that each piece of the (idealized in infinite resolution) graphic $\gsection(\dbasepoint)$ has a corresponding data value $\vindexpull\dsection(\dbasepoint)$.
  \label{fig:atct:morphisms:sheaf}}
\end{figure}

@@

 \begin{equation}
  \label{eq:atct:sheaves:homset}
  \begin{tikzcd}
    \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} 
    \arrow[dd, "\textcolor{set}{Hom}_{\sheafc_{\dbasec}}"', color=homset] 
    \arrow[rrdd, "\textcolor{set}{Hom}_{\sheafc_{\dbasec},\sheafc_{\gbasec}}", color=homset] 
    \arrow[rr, "\vindexpullc", color=functor] &  &
    \cgamma{\opensetgc}{\vindexpullc\dtotalc\restriction_{\opensetgc}} 
    \arrow[dd, "\textcolor{set}{Hom}_{\sheafc_{\gbasec}}", color=homset] \\
     & & \\
    \cgamma{\opensetc}{\vindexpushc\gtotalc\restriction_{\opensetc}} &  & 
    \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} 
    \arrow[ll, "\vindexpushc"', color=functor]                  
    \end{tikzcd}
\end{equation}

@@

\section{Objects & Functions}
This table contains a summary of the topological structures introduced in \autoref{sec:atct:fiber-bundles} and \autoref{sec:construction:vtotal} and what they encode. These structures serve as the basis of abstractions for the data objects in \autoref{sec:discussion}.

\begin{table}[h]
  \centering
  \begin{tabular}{|r|r|r|r|r|}
    \hline\\
   & Data  & Visual  & Graphic  & Encodes \\
\hline \\
\textcolor{total}{total space} & \dtotal & \vtotal & \gtotal &  \\
\hline\\
\textcolor{base}{base space} & \dbase & \dbase & \gbase & topological structure\\
\hline \\ 
\textcolor{base}{open set} & \openset & \openset & \opensetg & subspace \\
\hline \\
\textcolor{fiber}{fiber space} & \dfiber & \vfiber & \gfiber  & field structure\\
\hline \\
\textcolor{section}{Section} & \dsection & \vsection & \gsection & data set \\
\hline
  \end{tabular}
\end{table}

@@

>>>>

\subsubsection{Example: Graphic and Data}
\begin{figure}[h!]
  \includegraphics*[width=1\columnwidth]{xi_scatter.png}
  \caption{The functors $\vindex, \vindexpull, \vindexpush$ establish the correspondence between a data section \dsection\ and a graphic generation function \gsection. For every data record $\dsection(\dbasepoint)$, there is a graphic generating function $\vindexpush\gsection = \gsection|_{\vindexpre\dbasepoint}$. This curried function is here represented as the visual parameters associated with that function to demonstrate that it generates the visual element for that data record. Every data section can also be copied over to the graphic space such that each piece of the (idealized in infinite resolution) graphic $\gsection(\dbasepoint)$ has a corresponding data value $\vindexpull\dsection(\dbasepoint)$.
  \label{fig:atct:morphisms:sheaf}} \note{possibly reorient and expand this diagram to illustrate eq 55}
\end{figure}

@@

 \note{should either be oriented same as 55 and/or pushed back up to 3.3 as an intro to artist or squished a little. }
 \begin{equation}
  \label{eq:atct:sheaves:homset}
  \begin{tikzcd}
    \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} 
    \arrow[dd, "\textcolor{set}{Hom}_{\sheafc_{\dbasec}}"', color=homset] 
    \arrow[rrdd, "\textcolor{set}{Hom}_{\sheafc_{\dbasec},\sheafc_{\gbasec}}", color=homset] 
    \arrow[rr, "\vindexpullc", color=functor] &  &
    \cgamma{\opensetgc}{\vindexpullc\dtotalc\restriction_{\opensetgc}} 
    \arrow[dd, "\textcolor{set}{Hom}_{\sheafc_{\gbasec}}", color=homset] \\
     & & \\
    \cgamma{\opensetc}{\vindexpushc\gtotalc\restriction_{\opensetc}} &  & 
    \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} 
    \arrow[ll, "\vindexpushc"', color=functor]                  
    \end{tikzcd}
\end{equation}

@@

\section{Summary}
This table contains a summary of the topological structures introduced in \autoref{sec:atct:fiber-bundles} and \autoref{sec:construction:vtotal} and what they encode. These structures serve as the basis of abstractions for the data objects in \autoref{sec:discussion}.

\begin{table}[h]
  \centering
  \begin{tabular}{|r|r|r|r|r|}
    \hline
   & Data  & Visual  & Graphic  & Encodes \\
\hline 
\textcolor{total}{total space} & \dtotal & \vtotal & \gtotal &  \\
\hline
\textcolor{base}{base space} & \dbase & \dbase & \gbase & topological structure\\
\hline 
\textcolor{base}{open set} & \openset & \openset & \opensetg & subspace \\
\hline 
\textcolor{fiber}{fiber space} & \dfiber & \vfiber & \gfiber  & field structure\\
\hline 
\textcolor{section}{Section} & \dsection & \vsection & \gsection & data set \\
\hline
  \end{tabular}
\end{table}

@@

\note{color and replace source/target with constraint}
\begin{table}[h]
  \centering
\begin{tabular}{|r|l|r|r|}
  \hline
      & function & source & target \\
  \hline
  \textcolor{artist}{artist} & $\vartist: \Gamma(\dbase, \dtotal) \rightarrow \Gamma(\gbase, \gtotal)$ &  data & graphic \\
  \hline 
  \textcolor{functor}{lookup} & $\vindex: \gbase\rightarrow \dbase$ & graphic space & data space\\
  \hline
  \multicolumn{4}{c}{}\\
  \hline
  \textcolor{artist}{encoder} & $\vchannel: \Gamma(\dbase, \dtotal) \rightarrow \Gamma(\dbase, \vtotal) $ & data & visial \\
  \hline
  \textcolor{artist}{compositor} & $\vmark: \Gamma(\dbase,\vtotal) \rightarrow \Gamma(\gbase, \vtotal)$ & visual & graphic \\
  \hline
\end{tabular}
\end{table}

These functions can be verified using the following functions:
